Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-08-26 main_new.tex
updates

River plumes belong to a class of ocean processes that are local and
at smaller \emph{sub-mesoscale}, from 10 m -- 5 km where spatial
lateral variability tends to dominate. Remote sensing and synthetic
ocean models find it challenging to provide detail at this scale
\citep{Lermusiaux:2006} and the principal way to resolve for fine
resolution is by direct observation. At larger \emph{mesoscale}
($>50 km^2$), both three-dimensional space and time dynamics are
important and can shift substantially, while in the case of river
plumes one can often limit scope to cover only lateral spatial
elements ([north, east] domain). Moreover, for this case, time-effects
can be regarded as static when acquiring AUV data over a short time
window and limited region. However, the methodological framework can
be extended to higher dimensional situations in a similar manner.

>>>>

River plumes belong to a class of ocean processes that are local and
at smaller \emph{sub-mesoscale} (from $10 m^2$ -- $5 km^2$ where
spatial lateral variability tends to dominate. Remote sensing and
synthetic ocean models find it challenging to provide detail at this
scale \citep{Lermusiaux:2006} and the principal way to resolve for
fine resolution is by direct observation. At larger \emph{mesoscale}
($>50 km^2$), both three-dimensional space and time dynamics are
important and can shift substantially, while in the case of river
plumes one can often limit scope to cover only lateral spatial
elements ([north, east] domain). Moreover, for this case, time-effects
can be regarded as static when acquiring AUV data over a short time
window and limited region. However, the methodological framework can
be extended to higher dimensional situations in a similar manner.
